Exploring the composition of lithic assemblages in Mesolithic south-eastern Norway

### 2021-06-11 analysis/paper/paper.Rmd
Began trying to tackle the conclusion

The results of the CA using the entirety of the lithic assemblages align more or less with results of previous research in south-eastern Norway. This would indicate that in general, meaningful chronological patterning is associated with the employed artefact categories. These tendencies are already well-established when it comes to the formal tool types, but have been given less focus in light of entire assemblages. Precisely what behavioural implication the development in the use of these types have, however, is less clear, but appears to follow a different, and more complex trajectory than that of curation, as operationalised here.

In my view this alignes well with the framework of @clark2017, suggesting that shifts in mobility patterns has caused this empirical pattern. However, the role of non-flint material, variability of flint quality. Furthermore, precisely how this mobility pattern has. Here Binfords model of briefly invoked, but there exists a wide range of possible configurations and mobility strategies that

>>>>

The results of the CA align more or less with results of previous research in south-eastern Norway. This would indicate that in general, meaningful chronological patterning is associated with the employed artefact categories. These tendencies are already well-established when it comes to the formal tool types, but have been given less focus in light of entire assemblages. Precisely what behavioural implication the development in the use and occurrences of the tool and debitage categories are less clear, but appears to follow a different, and more complex trajectory than that of curation, as operationalised herge.

The temporal trends associated with the curation index corresponds surprisingly well with trajectories of cultural development previously suggested in the literature, and does therefore, in my view, suggest that shifts in mobility patterns has caused this empirical pattern, in line with the framework of @clark2017. Another perspective would be that this is not surprising at all, and that its previously demonstrated relevance across a wide range of contexts rather points to its pervasive relevance for the organisation of lithic technology, and that there as a consequence should be little reason to think that a the setting of Mesolithic south-eastern Norway should be any different. In any case, if its applicability and relevance for this setting is accepted, the relationship does hold great potential for large scale comparative studies in Mesolithic Norway and beyond. Futhermore, while the temporal trends associated with the curation index was here narratively associated with the most immediate chronological trends that have frivolously been associated with the Mesolithic in south-eastern Norway, the explicit quanitiication offers the possibility of more formal comparisons with a wide range of environmental, demographic and cultural dimensions across multiple scales.

However, the role of non-flint material, variability of flint quality. Furthermore, precisely how this mobility pattern has. Here Binfords model of briefly invoked, but there exists a wide range of possible configurations and mobility strategies that
